Categorical Foundations of E-Graphs With Binding

### 2025-07-10 LICS_2025/e_graphs_with_bindings/sections/introduction.tex
Fix bibliography

Commonly, string diagrams are used informally to provide a two-dimensional syntax for the internal language of a category, but for our purposes we must be more formal. 
Specifically, we require a concrete encoding of string diagrams, analogous to the de Bruijn index representation of $\lambda$-terms.
For this, we use \emph{hypergraphs}~\cite{bonchi_string_2022-1}, which have nice syntactic characteristics for this purpose.
For instance, hypergraphs admit the property that two string diagrams are equal if and only if they ``look the same'' (\emph{i.e.} they admit a graph isomorphism); secondly, string-diagrammatic equational reasoning can be formalised as (categorical) graph rewriting using the technique of double-pushout rewriting (DPO)~\cite{1011453502719}.

>>>>

Commonly, string diagrams are used informally to provide a two-dimensional syntax for the internal language of a category, but for our purposes we must be more formal. 
Specifically, we require a concrete encoding of string diagrams, analogous to the de Bruijn index representation of $\lambda$-terms.
For this, we use \emph{hypergraphs}~\cite{bonchi_string_2022-1}, which have nice syntactic characteristics for this purpose.
For instance, hypergraphs admit the property that two string diagrams are equal if and only if they ``look the same'' (\emph{i.e.} they admit a graph isomorphism); secondly, string-diagrammatic equational reasoning can be formalised as (categorical) graph rewriting using the technique of double-pushout rewriting (DPO)~\cite{bonchi_string_2022-1}.

### 2025-07-10 POPL2026/paper/sections/introduction.tex
Fix bibliography

Commonly, string diagrams are used informally to provide a two-dimensional syntax for the internal language of a category, but for our purposes we must be more formal.
Specifically, we require a concrete encoding of string diagrams, analogous to the de Bruijn index representation of $\lambda$-terms.
For this, we use \emph{hypergraphs}~\cite{bonchi_string_2022-1}, which have nice syntactic characteristics.
For instance, hypergraph isomorphism captures when string diagrams \enquote{look the same} --- topologically, that one may be deformed continuously into the other without obstruction\footnote{This is the informal notion of the \enquote{isotopy of string diagrams}.}; secondly, string-diagrammatic equational reasoning can be formalised as (categorical) graph rewriting over these hypergraphs using the technique of double-pushout rewriting (DPO)~\cite{1011453502719}.

>>>>

Commonly, string diagrams are used informally to provide a two-dimensional syntax for the internal language of a category, but for our purposes we must be more formal.
Specifically, we require a concrete encoding of string diagrams, analogous to the de Bruijn index representation of $\lambda$-terms.
For this, we use \emph{hypergraphs}~\cite{bonchi_string_2022-1}, which have nice syntactic characteristics.
For instance, hypergraph isomorphism captures when string diagrams \enquote{look the same} --- topologically, that one may be deformed continuously into the other without obstruction\footnote{This is the informal notion of the \enquote{isotopy of string diagrams}.}; secondly, string-diagrammatic equational reasoning can be formalised as (categorical) graph rewriting over these hypergraphs using the technique of double-pushout rewriting (DPO)~\cite{bonchi_string_2022-1}.
